% ---------------------------------------------------------------------
% Front matter, Springer-monograph style: half-title, full title page
% (dark navy panel matching the website book card), and a colophon /
% copyright page. Injected by pandoc as include-before-body, so it runs
% after \frontmatter and before \tableofcontents. Uses \clearpage only
% (never \cleardoublepage) so the one-sided layout adds no blank pages.
% ---------------------------------------------------------------------

% ---------- Half-title ----------
\thispagestyle{empty}
\vspace*{0.30\textheight}
\begin{center}
{\sffamily\bfseries\fontsize{24}{28}\selectfont\color{brandSlate}%
 Space-Based AI Data Centers}\\[10pt]
{\sffamily\itshape\large\color{brandTeal}%
 An Engineering Study}
\end{center}
\clearpage

% ---------- Title page (designed panel) ----------
\thispagestyle{empty}
\vspace*{0.4cm}
\begin{center}
\begin{tcolorbox}[colback=spaceNavy, colframe=spaceNavy, arc=8pt,
  boxrule=0pt, left=26pt, right=26pt, top=30pt, bottom=30pt, width=\textwidth,
  enhanced, borderline south={4pt}{0pt}{brandTeal}]
\raggedright
{\sffamily\bfseries\footnotesize\color{white!75!brandTeal}%
 \fcolorbox{white!25!spaceNavy}{white!12!spaceNavy}{\strut~EDITION I\,\textbullet\,ENGINEERING STUDY\,\textbullet\,2026~}}\\[26pt]
{\sffamily\bfseries\fontsize{34}{38}\selectfont\color{white}%
 Space-Based\\ AI Data Centers}\\[10pt]
{\sffamily\itshape\Large\color{brandTeal!75!white}%
 Physics, Mathematics, Simulation, and Economics\\ of an Orbital Compute Constellation}\\[30pt]
{\sffamily\normalsize\color{white!80!spaceNavy}%
 A primary-source engineering study of the orbital data-center concept,\\
 from orbital mechanics and thermal control to debris survivability,\\
 launch economics, and a fully open simulation model.}
\end{tcolorbox}

\vfill

{\sffamily\Large\bfseries\color{brandSlate} Samarjith Biswas, PhD}\\[4pt]
{\sffamily\normalsize\color{brandGray} Research Scientist III}\\[16pt]
{\sffamily\small\color{brandGray}%
 samarjithbiswas.com\,\textbullet\,Research Portfolio and Open Toolkits}
\end{center}
\clearpage

% ---------- Colophon / copyright ----------
\thispagestyle{empty}
\vspace*{\fill}
\noindent{\sffamily\small\color{brandGray}%
\textbf{\color{brandSlate}Space-Based AI Data Centers: Physics, Mathematics, Simulation, and Economics.}\\[2pt]
Edition I, 2026. By Samarjith Biswas, PhD.\\[10pt]
This work is released open access. The accompanying source code is licensed under the MIT License;
the text, figures, and equations are licensed under Creative Commons Attribution 4.0 (CC-BY 4.0).
You are free to read, share, cite, and adapt the work with attribution.\\[10pt]
Source repository (models, derivations, simulations, figures):\\
\texttt{github.com/Samarjithbiswas/space-based-ai-datacenter}\\[6pt]
Reference architecture: Google Project Suncatcher, arXiv:2511.19468.\\[10pt]
Every figure and every load-bearing number in this book is regenerated by the open repository.
Forward-looking quantities, including the launch-cost trajectory of Chapter 22, are presented as
projections with explicit uncertainty bands, not as guarantees. Independent reproduction and
correction are welcome.\\[10pt]
Typeset in IBM Plex Sans and IBM Plex Mono with pdf\LaTeX.\\[2pt]
Part of the samarjithbiswas.com research portfolio.
}
\clearpage
